Supplementary Information: Global patterns of forest autotrophic carbon fluxes

### 2020-02-18 manuscript/appendix.Rmd
corrected figure numbering

```{r setup, include = FALSE}
knitr::opts_knit$set(root.dir = 'C:/Users/becky/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/')
# knitr::opts_knit$set(root.dir = '/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/Global_Productivity/manuscript/')
```

@@

```{r echo=FALSE, fig.cap = "Figure S2: Individual plots of FACF in relation to mean annual climate, part 1.", out.width='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S3: Individual plots of FACF in relation to mean annual climate, part 2.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.cap = "Figure S4: Individual plots of FACF in relation to mean climate seasonality, part 1.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S5: Individual plots of FACF in relation to mean climate seasonality, part 2.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S6: Growing season length-standardized FACF in relation to mean growing season climate, part 1.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S7: Growing season length-standardized FACF in relation to mean growing season climate, part 2.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S8: Ratios among FACF as a function of latitude and climate variables", out.width ='100%', fig.pos='H'}

>>>>

```{r setup, include = FALSE}
# knitr::opts_knit$set(root.dir = 'C:/Users/becky/Dropbox (Smithsonian)/GitHub/Global_Productivity/manuscript/')
knitr::opts_knit$set(root.dir = 'C:/Users/gyrcbm/Dropbox/Global_Productivity/manuscript/')
# knitr::opts_knit$set(root.dir = '/Users/kteixeira/Dropbox (Smithsonian)/GitHub/ForC-db/Global_Productivity/manuscript/')
```

@@

```{r echo=FALSE, fig.cap = "Figure S3: Individual plots of FACF in relation to mean annual climate, part 1.", out.width='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S4: Individual plots of FACF in relation to mean annual climate, part 2.", out.width='100%', fig.pos='H'}

@@

```{r echo=FALSE, fig.cap = "Figure S5: Individual plots of FACF in relation to mean climate seasonality, part 1.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S6: Individual plots of FACF in relation to mean climate seasonality, part 2.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S7: Growing season length-standardized FACF in relation to mean growing season climate, part 1.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.cap = "Figure S8: Growing season length-standardized FACF in relation to mean growing season climate, part 2.", out.width ='100%', fig.pos='H'}

@@

\newpage
```{r echo=FALSE, fig.align = "center", fig.cap = "Figure S9: Ratios among FACF as a function of latitude and climate variables", out.width ='100%', fig.pos='H'}
